PS753 Glossary

### 2022-02-01 _academics/ps753-glossary/ps753-glossary.Rmd
Add week 2 terms

>>>>

## Week 2

### Class lecture 2a: [Network Structure - Walks, Paths, and Distance](https://www.loom.com/share/a8a7949244f04ed5995d572340c20aa0)

Connections between nodes:

adjacent
: a direct connection between nodes; not necessarily bilateral in directed networks. A leading to B ("A adj B") does not mean that B leads to A ("B adj A)

reachable
: whether a node is reachable from another node, regardless of distance

distance
: the number of ties (steps, edges) that must be traversed to reach a target node

walk
: sequence (not *path*, see below) that connects two nodes, consisting of the nodes and edges

trail
: a walk that can only go through each edge / tie once, but can hit the same node more than once

path
: a trail that only hits each node and edge once; the start and end node may be the same

geodesic distance
: the shortest path between two nodes; by definition, not a trail or walk because repeated segments wouldn't be the shortest; with binary data, the number of steps; with weighted data, might be a sum or some other calculation of "effort"

### Class lecture 2b: [Graph Substructures and Components](https://www.loom.com/share/515068ae6dc641be984c0ef974fb8e52)

Network substructures

dyad, triad, clique
: two, three, or four-or-more connected nodes

complete graph
: a network where every node is directly connected to every other node

connected graph
: a network where every node is indirectly connected to every other node

unconnected graph
: a network where at least one node is unreachable

component
: the set of all points that constitutes a connected subgraph within a network

main component
: the largest component within a network

minor component
: a smaller one, possibly one of many

pendant
: a node with only one link or edge to a network, "dangling"

isolate
: an unconnected node

### Class lecture 2c: [Dyad and Triad Census](https://www.loom.com/share/96aaf1d2982d427c83564c338d2e0b83)

mutual dyad
: a dyad where both nodes connect to each other, as in an undirected network

asymmetric dyad
: a dyad (in a directed network) where one node connects to another, but non-reciprocally (one way only)

null
: a dyad of two unconnected nodes

(empty / one edge / two path / triangle) triad
: a triad with zero, one, two or three edges between three nodes (all four possible permutations)

balance theory
: the theory that two nodes connected to a common node will also develop connections to each other

global transitivity index
: the proportion of triads in a network that are complete (with 3 connections between them)

There is a vocabulary for triads in directed networks describing the 16 possible permutations of ties (or the absence thereof) among 3 nodes, counting the number of mutual, asymmetric and null dyads, with direction indicators, like `003` or `120D` - see the slide at 3:45

vacuously transitive triad
: a triad where (5 of 16 possibilities)

intransitive triad
: a triad where (7 of 16 possibilities)

transitive triad
: a triad where (4 of 16 possibilities)

xxx see https://corescholar.libraries.wright.edu/cgi/viewcontent.cgi?article=2427&context=knoesis

### Class lecture 2d: [Transitivity and Clustering Coefficient](https://www.loom.com/share/ff29331e900741dd8634d921e4abafdc)

local transitivity / local clustering coefficient
: the likelihood that the neighbors of a node are also connected to each other; the number of connections that *do* exist over the number of connections that *could* exist
